---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
library(ISLR)
data(Hitters)
head(Hitters)
data <- na.omit(Hitters)

library(glmnet)
names(data)
X=model.matrix(Salary~.,data)[,-1]
y=data$Salary

```

```{r}

sh <- 10^seq(10,-2,length=100)
Ridge <- glmnet(X,y,alpha=0, lambda=sh)
summary(Ridge)
Lasso <- glmnet(X,y, alpha=1, lambda=sh)
summary(Lasso)

par(mfrow=c(1,2))
plot(Ridge)
plot(Lasso)

```

```{r}

CrossValidError = cv.glmnet(X,y,alpha=0)
plot(CrossValidError)
CrossValidError$lambda.min
coef(CrossValidError)
```

